Temporary Trade Barriers: \\ When Will They End?

### 2017-10-27 presentation.tex
simplify uncertainty slide

\begin{frame}{What's this uncertainty about?}
\pause
Lobby must be able to trigger the original AD duty
\begin{itemize}[<+->]
	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
	\item It could be justified, not motivated by politics/rent-seeking
	\item But still, firms lobby for duties they don't get
\end{itemize}

\pause
\vskip.1in
So what's the uncertainty about?
\pause
\begin{itemize}[<+->]
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
\end{itemize}

@@

\begin{frame}{Feedback, Comments from InsTED presentation}
\begin{itemize}[<+->]
	\item Could leverage 5-year renewal cycle vs. 4-year re-election cycle (Sarah Danzman, Indiana U)
	\item Look for Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
	\item Need to have first stage (Jee-Hyeong, Gary Lyn)
		\begin{itemize}
			\item Look at Park and Blonigen (Jee-Hyeong)
			\item Cost differential for firms to get initial duty vs. renewal?
			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
		\end{itemize}
	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
\end{itemize}

>>>>

\begin{frame}{What's this uncertainty about?}
\pause
\begin{itemize}[<+->]
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
\end{itemize}

@@

\begin{frame}{Feedback, Comments from InsTED presentation}
\begin{itemize}[<+->]
	%\item Could leverage 5-year renewal cycle vs. 4-year re-election cycle (Sarah Danzman, Indiana U)
	\item Look for Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
	\item Need to have first stage (Jee-Hyeong, Gary Lyn)
		\begin{itemize}
			\item Look at Park and Blonigen (Jee-Hyeong)
			\item Cost differential for firms to get initial duty vs. renewal?
			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
		\end{itemize}
	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
\end{itemize}
